dispRity metrics

### 2015-10-15 doc/dispRity-metrics.Rnw
added metric implementation details

\section{metric argument in \dispRity}
Of course, functions can be more complex and involve multiple operations such as the \texttt{centroids} function (see \texttt{?dispRity.metric}) that calculates the euclidean distance between each elements and the ordinated space centroid.
The \texttt{make.metric} function implemented in \dispRity is designed to help testing and finding the level of the functions.
Concretely, This function tests:
\begin{enumerate}
  \item if your function can deal with a matrix as an \texttt{input}.
  \item which level is your function (level 1, 2 or 3, see \texttt{?dispRity.metric}).
  \item whether the function can properly be implemented in the \texttt{dispRity} function.
\end{enumerate}
For example, let's see if the functions described above are the right levels:

>>>>

\section{metric argument in \dispRity}
Using this metric structure, on can easily use any disparity metric in the \dispRity function as follows:

<<dispRity example>>=
## First we need to load the data
data(BeckLee_mat50)
## Measuring disparity as the standard deviation of all the value of the ordinated
## matrix (level 1 function).
summary(dispRity(BeckLee_mat50, metric = sd))
## Measuring disparity as the standard deviation of the variance of each axis of
## the ordinated matrix (level 1 and level 2 functions).
summary(dispRity(BeckLee_mat50, metric = c(sd, variances)))
## Measuring disparity as the standard deviation of the variance of each axis of
## the variance covariance matrix (level 1, level 2 and level 3 functions).
summary(dispRity(BeckLee_mat50, metric = c(sd, variances, var)), round=10)
## Note that the order of each function in the metric argument does not matter,
## the algorithm always classifies them by levels and computes first level 3,
## then level 2 and finally level 1.
summary(dispRity(BeckLee_mat50, metric = c(variances, sd, var)), round=10)
## Both ways output the same disparity values.
@
